Generating exact lattices in a WFST framework

### 2011-09-26 misc/papers/icassp12_lat/paper.tex
Improved affiliations on paper
git-svn-id: https://svn.code.sf.net/p/kaldi/code/trunk@512 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother
\name{ Daniel Povey$^1$, Mirko Hannemann$^2$,  \\
  {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^4$, {Arnab Ghoshal}$^6$, {Milos Janda}$^2$, {Stefan Kombrink}$^2$, \\
  {Petr Motl\'{i}\v{c}ek}$^7$, {Yanmin Qian}$^8$, {Ngoc Thang Vu}$^9$, {Korbinian Reidhammer}$^10$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks here}}
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother

@@

\address{$^1$ Microsoft Research, Redmond, WA, {\normalsize \tt dpovey@microsoft.com} \\
         $^2$ Brno University of Technology, Czech Republic, {\normalsize \tt \{karafiat,schwarzp\}@fit.vutbr.cz} \\
         $^3$ Saarland University, {\normalsize \tt arnab.ghoshal@lsv.uni-saarland.de} }

>>>>

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother
\name{ Daniel Povey$^1$, Mirko Hannemann$^2$,  \\
  {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^4$, {Arnab Ghoshal}$^5$, {Milos Janda}$^2$, {Stefan Kombrink}$^2$, \\
  {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Ngoc Thang Vu}$^8$, {Korbinian Reidhammer}$^9$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks here}}
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother

@@

\address{$^1$ Microsoft Research, Redmond, WA, {\normalsize \tt dpovey@microsoft.com} \\
         $^2$ Brno University of Technology, Czech Republic, {\normalsize \tt ihannema@fit.vutbr.cz} \\
         $^3$ CRIM, Montreal, Canada \ \  $^4$ SRI International, Menlo Park, CA, USA \\
         $^5$ University of Edinburgh, U.K. \ \  $^6$  IDIAP, Martigny, Switzerland  \\
         $^6$ Shanghai Jiao Tong University, China \ \ $^7$ Karlsruhe Institute of Technology, Germany \\
         $^9$ Friedrich Alexander University of Erlangen-Nurnberg, Germany}
